Comprehensive Quality-Aware Automated Semantic Web Service Composition

### 2017-01-29 paper.tex
update

\begin{document}
\maketitle
\begin{abstract}
Semantic web service composition has been a prevailing research area in recent years. There are two major challenges faced by researchers, semantic matchmaking and QoS optimisation. Semantic matchmaking aims to discover interoperable web services that can interact with each other to provide rich functionalities through language understanding and reasoning. QoS optimisation aims to optimise the non-functional requirement of service users, e.g., minimum cost, maximal reliability. Many scholars have looked into QoS optimisation problems in QoS-aware web service composition applying AI planning and Evolutionary Computation techniques. To meet users' requirement, one often needs to consider both semantic matchmaking quality and QoS simultaneously. Existing works on web service composition often concerns either semantic service composition or QoS-aware service composition. However, there are few works concerns both semantic matchmaking quality and QoS at the same time and achieve a more 
desirable tradeoff in consideration of both sides. Therefore, In this paper, proposed a genral comprehensive quality model that can achieve a more desirable balance in consideration of both semantic matchmaking quality and QoS. This model is also suitable to be tackled through EC algorithms, and we develope a PSO-based service composition approach with explicit support for the comprehensive model, which can generate more desiable balanced web service composition that meet both senmantic matchmaking quality and QoS requirement by comparing existing QoS evaluation model using benchmark dataset. We also conduct an experiment shows our PSO-based mehtod performs better in finding more optimised solution by comparing one existing GP-based method.

@@

The overall goal of this paper is to \textit{develop an comprehensive appraoch to automated QoS-aware semantic web service composition that satisfactorily optimises both QoS and semantic matchmaking quality}. Particularly, this paper extends existing works of QoS-aware service composition by considering both QoS optimisation and semantic matchmaking quality optimisation in our proposed comprehensive quality model. Particle Swarm Optimisation (PSO) has show its promise in searching near-optimised service composition solutions \cite{da2016particle}. We will propose a PSO-based service composition approach using our comprehensive quality model to measure semantic matchmaking in automated semantic web service composition. We will achieve three objectives in this work as follows:

@@

 \item To evaluate our proposed approach, we conduct experiment to compare our comphensive quality model with QoS evaluation model, we also compare an one existing GP approach with our appraoch using our comprehensive model. Both comparison utilise benchmark datasets from Web Services Challenge 2009 (WSC09) \cite{kona2009wsc}

@@

\section{Related Work} \label{relatedWork}
Substantial work on web service composition either focused on semantic web service composiiton \cite{boustil2014semantic,mier2015integrated, bansal2016generalized} or QoS-aware web service composiiton \cite{da2016particle,da2015graphevol,yu2013adaptive, gupta2015optimization,qi2010combining}, However few researchers addressed both semantic mathmaking quality and QoS requirements at the same time for web service composition problems. To the best of our knowledge, \cite{lecue2009optimizing,fanjiang2014semantic,pop2009immune} reported some recent attempts on service composition that considers both aspects.

\cite{boustil2014semantic,mier2015integrated, bansal2016generalized} captures the semantics of the parameters of web services using some kind of logic (e.g., description logic) for enabling semantic web service composition, where the number of web servces or length of the graph is minimised to reach the optimised graph-based compositin solutions. However, these approaches always need to improve their scalability for a large number of web services, and the evalution method does not fit for today's customers' requirements properly.

@@

Evolutionary Computation (EC) techniques are used to improve the scalability for solving NP-hard problems. Gupta et al. \cite{gupta2015optimization} employ an Genetic Algorithm to the problem of QoS-ware web service composition, and a set of binary strings are used as individuals, which demands to be decoded into composition solutions. Genetic Programming are employed by  \cite{yu2013adaptive} with direct reprentation of compsotion solutions, the overall quality of solutions are measured by a fitness function that is liable for penalising infeasible solutions. A hyper approach employs both a greedy search algorithm and Genetic Programming (GP) is introduced in \cite{ma2015hybrid} to generate locally optimised solution with functionality correctness. In particularly, the greedy search is used to generate directed acrylic graph as composition solutions, which is further transferred to tree structure using unfolding techniques for initialisation and mutation during the evolutionary process. To eliminating the transformation process from DAG, A promising GraphEvol is proposed in \cite{da2015graphevol}, where web service composition are in a form of Directed Acyclic Graph(DAG) employing Graph-based evolutionary operators like crossover and mutation. PSO has shown its efficiency in solving combinatorial optimisation problems \cite{fukuyama2008fundamentals}, an indirect PSO-based approach was introduced in \cite{da2016particle}. An opimised queue is used as indirect representation as composition solution that decoding into Direct Acyclic Graph (DAG). These QoS-aware appraoches does not consider semantic matchmaking quality, which could lead to over-general outputs to be produced by selected services, The finding is evidently supported by our first comparision experiment. In fact, customers' perspectives, application domains and ontology granularity all could have significant impact on the outputs requested by users. In some scenarios, the output is too broad to bear any specific meaning for the customers, even though those web services selected leads to a very good overall QoS.

Few works \cite{lecue2009optimizing,fanjiang2014semantic,pop2009immune} employ EC technique for considering both semantic matchmaking quality and QoS simultaneously. Lecue et al. \cite{lecue2009optimizing} employ Genetic Algorithm for semi-automated web service composition considering semantic matchmaking quality and QoS, where the semantic matchmaking quality is measured the quality of semantic links that requires formal definition of ontology in Description logic. This evaluation takes huge cost and time for the domain experts to establish required ontology. Another GA-based appraoch work \cite{fanjiang2014semantic} employs a sequence of fitness functions are used in the binary selection of chromosomes, where semantic matchmaking quality is evaluate in two fitness functions considering concept similarity and parameter similarity respectively, However, different semantic matchmaking types are ignored in evaluation model. The work \cite{pop2009immune} as an immune-inspired web service composition approach employ indirect reprentation that a binary alphabet to encode a planning graph, where the semantic matchmaking quality is measured  by the similarity using information retrieval technique.

In summary, composition solutions from semantic web service composition does not consier QoS \cite{boustil2014semantic,mier2015integrated, bansal2016generalized}, and QoS-aware web service composiiton \cite{da2016particle,da2015graphevol,yu2013adaptive, gupta2015optimization,qi2010combining} does not consider distinguished matchmaking quality in their fitness function. Few works do consider both quality aspects, but some limitatins lie in semi-automated approach \cite{lecue2009optimizing}, less general semantic quality measurement \cite{lecue2009optimizing, pop2009immune}, or semantic matchmaking types ignorance \cite{pop2009immune}. In addition, experiments design for  \cite{lecue2009optimizing,fanjiang2014semantic,pop2009immune} are not conducted using benchamark dataset for the scalability, only small datasets are utilised that might suffer scalability. Results analysis for \cite{lecue2009optimizing,fanjiang2014semantic,pop2009immune} also do not evidently point out what desired balance could be rearched by considering semantic matchmaking quality and QoS. Therefore, we proposed a general comprehensive quality model which achieve a more desirable balance in consideration of both semantic matchmaking quality and QoS to fill the gaps dissussed above, and then we proposed a POS-based method with explicit support for the comprehensive model, and evaluate its performace by comparing with one existing GP-based approach.

@@

\subsection{Quality of Service and Composition Constructs}\label{Quality of Service and Composition Constructs}
According to \cite{zeng2003quality}, four most often considered QoS parameters are response time, cost, reliability and availability decribed as follows:
\begin{itemize}
\item \textit{Response time} ($T$) measures the expected delay in seconds between the moment when a request is sent and the moment when the results are received.
\item \textit{Cost} ($C$) is the amount of money that a service requester has to pay for executing the web service
\item \textit{Reliability} ($R$) is the probability that a request is correctly responded within the maximum expected time frame.
\item \textit{Availability} ($A$) is the probability that a web service is accessible.
\end{itemize}
The aggregation value of QoS attributes for a composite service varies with respect to different constructs, which reflects how services associated with each other in a service composition \cite{zeng2003quality}. Here we consider two composition constructs: sequence and parallel constructs, in building the composition web service. The QoS calculation models are described as follows:
\subsubsection{Sequence construct}
The composition web service executes each atomic service associated with a sequence construct in a definite sequence order. The aggregation value for total time ($T$) and total cost ($C$) is as the sum of time and cost of web services involved respectively. The overall availability and reliability in a sequence construct are calculated by multiplying their corresponding availability and reliability of each web service in probability theory. This construct is shown in Fig. \ref{sequence}.
\subsubsection{Parallel construct}
Web services in a parallel construct are executed concurrently. The QoS aggregation value for total cost, availability and reliability are the same as these in sequence construct while the Total time ($T$) is determined by the most time-consuming path in the composition flow of the solution. This construct is presented in Fig. \ref{parallel}.

@@

\textbf{Semantic web service link quality model}. Due to the discretisational characteristics of different match types and values assigned to matching types that driven by the cost of data integration and manipulation \cite{lecue2009optimizing}, partial ordering match types are considered to be one factor for quality of parameter matchmaking, denoted as $mt_{p}$,  For example, Exact matching type demands less time for computation compared to that of Plugin match. Another factor in our proposed model is concept similarity, which could be evaluated based on the edge counting method defined in \cite{shet2012new}. This formula (\ref{equation1}) is used to estimate the concept similarity between matching parameters, which is denoted as $s_{p}$. Therefore, given the quality of parameter matchmaking type and quality of parameter concept similarity, the quality of parameter matchmaking is defined by Formula (\ref{equation2}), where the value of $mt_{p}$ follows the same settings in \cite{lecue2009optimizing}. Particularly, 1 (Exact), 0.75 (Plugin), 0.5 (Subsume) or 0.25 (Intersection).

\begin{equation}
q(p_ {s}){=} \frac{2N \cdot e^{-\lambda L/D} }{N_{1}+N_{2}}
\label{equation1}
\end{equation}

@@

\section{Results and Analysis}\label{results_analysis}
\subsection{Comparison Test with QoS Evaluation Model}\label{comparisonTest}
In this section, we analyse the composition solution generated by using our approach comparing with QoS-aware approach. First, we look at mean value of $Q_{mt}$, $Q_{s}$ and $Q_{QoS}$ at optimum at the 100th generation for two approaches, shown in Table \ref{decisionTable}. The QoS-aware approach record $Q_{mt}$, $Q_{s}$ and utilise fitness function $Fitness = w_1 \hat{A} + w_2 \hat{R} + w_3(1 - \hat{T}) + w_4(1 - \hat{C})$ when $\sum_{i=1}^{4} w_i = 1$, but $MT$ and $S$ are recorded, and $Q_(QoS)$ is normalised from 0 to 0.5 to make it comparable to $Q_{QoS}$ in our approach. We observe an interesting pattern from Table \ref{decisionTable} using statistic analysis: mean value of $Q_{mt}$ and $Q_{s}$ at optimum by our approach is consistently higher than those by QoS-aware approach.  Meanwhile, $Q_{QoS}$ generated by QoS-aware approach can obtain a slightly higher value than that of our approach. In conclusion, we can perceive that our evaluation could find out better functional quality with a reasonable trade off in QoS.
\begin{table}[]
\footnotesize
\centering
\caption{Mean Quality for comprehensive quality-aware methods and QoS-aware approach}
\label{decisionTable}
\begin{tabular}{l|l|l|l}
\hline
\multicolumn{2}{c|}{WSC09}              & \shortstack{QoS-aware \\ Evaluation} & \shortstack{Comprehensive \\ Quality Evaluation} \\ \hline
\multirow{3}{*}{Task1}  &$MT$   &0.189787 $\pm$ 0.039278686            &0.221862 $\pm$ 0.009582 $\uparrow$ \\ \cline{2-4} 
                        &$S$    &0.884962 $\pm$ 0.014140               &0.894082 $\pm$ 0.009206 $\uparrow$ \\ \cline{2-4}
                        &$QoS$  &0.278730 $\pm$ 0.007786               &0.280222 $\pm$ 0.008212                          \\ \hline
\multirow{3}{*}{Task2}  &$MT$   &0.001795 $\pm$ 0.000719               &0.001977 $\pm$ 0.001566 $\uparrow$ \\ \cline{2-4} 
                        &$S$    &0.906971 $\pm$ 0.005855               &0.923970 $\pm$ 0.006898 $\uparrow$   \\ \cline{2-4}
                        &$QoS$  &0.239979 $\pm$ 0.000578 $\uparrow$    &0.238596 $\pm$ 0.001264 \\ \hline
\multirow{3}{*}{Task3}  &$MT$   &0.158526 $\pm$ 0.014028               &0.245830 $\pm$ 0.007761 $\uparrow$   \\ \cline{2-4} 
                        &$S$    &0.949109 $\pm$ 0.002331               &0.972765 $\pm$ 0.002980 $\uparrow$           \\ \cline{2-4}
                        &$QoS$  &0.247002 $\pm$ 0.000661 $\uparrow$    &0.245631 $\pm$ 0.000431            \\ \hline
\multirow{3}{*}{Task4}  &$MT$   &0.000000 $\pm$ 0.000000               &0.000004 $\pm$ 0.000002 $\uparrow$ \\ \cline{2-4} 
                        &$S$    &0.879514 $\pm$ 0.007456               &0.920733 $\pm$ 0.000001 $\uparrow$ \\ \cline{2-4}
                        &$QoS$  &0.242297 $\pm$ 0.000507 $\uparrow$    &0.236677 $\pm$ 0.002211  \\ \hline
\multirow{3}{*}{Task5}  &$MT$   &  0.000042 $\pm$ 0.000030             &0.000078 $\pm$ 0.000020 $\uparrow$           \\ \cline{2-4} 
                        &$S$    &  0.915933 $\pm$ 0.012888             &0.927678 $\pm$ 0.002578 $\uparrow$                 \\ \cline{2-4}
                        &$QoS$  & 0.238189 $\pm$ 0.000240 $\uparrow$      &  0.237485 $\pm$  0.000328  \\ \hline                                                   
\end{tabular}
\end{table}

Second, to compare the results generated from two evaluation approaches, we demonstrate an example solution that shows the differences in web services composition obtained through two different methods. Fig. \ref{comparisontest} $(1)$ and $(2)$ show two composition weighted graphs as the two optmised solutions to Task 3 with $(1)$ QoS-aware approach and $(2)$ Comprehensive quality-aware method respectively. Two approaches generate exactly the same service workflow structure where those service vertices and edges denoted in red are different. We make a comparison of the quality among these different edges ($e_1$ to $e4$) associated service vertices in terms of quality of semantic matchmaking and QoS attributes in Fig. \ref{comparisontest} $(3)$. We also look at $\Delta Q$ which reveals the amount of variation on quality between two methods, where the positive values means the benefits gained under our approach while the negative values means the trade-off. To demonstrate the benefits of the positive value, we analyse the smallest positive $\Delta Q$ corresponding to $e_4$ and demonstrate how the output and required input are different under two approaches in Fig. \ref{comparisontest} $(4)$. $Ser1640238160$ and $Ser1947554374$ are selected service vertices with output concept-related parameters $Inst795998200$ and $Inst582785907$ corresponding to two concepts $Con103314376$ and $Con2037585750$ respectively, and $Inst658772240$ are the required parameter related to concept $Con2113572083$. There exist $Inst795998200$ $\in$ $Con103314376$ $\sqsubseteq_{2}$ $Inst658772240$ $\in$ $Con2113572083$ and $Inst582785907$ $\in$ $Con2037585750$ $\sqsubseteq_{3}$ $Inst658772240$ $\in$ $Con2113572083$. It is obvious that our approach selects the service providing $Inst795998200$ that are closer to the users' requirements suggesting that our method can produce better semantic matchmaking quality.

@@

\subsection{Comparison Test with GP-based approach}\label{comparisonTestWithGP}
We compare one GP-based approach  \cite{ma2015hybrid} with our PSO method, where the individuals are tree structure with strict constrains transferred from a DAG employing unfolding techniques. We further mark all the service nodes in the tree representation with all their outgoing edges for considering semantic matchmaking quality, and those edges information are maintained correctly in the crossover and mutation. At last, we evaluate both semantic matchmaking quality and QoS simultaneously using the discussed the comprehensive quality model to investigate the performances of two approaches. To make a fair comparison with our PSO approach considering the same number of evaluations (3000 times), we adjust the parameters settings for GP approach \cite{ma2015hybrid} to 30 individual for 100 generations.

The Table \ref{meanFitness} shows the mean fitness values accomplished by two methods and Table \ref{meanTime} shows the average execution time required by them. We employ statistical analysis to test the significant differences in mean fitness value and execution time.  The results show that the PSO-based approach performs better in four of five tasks. However, there is also a trade-off between optimised solution and execution time. We can see the PSO-based approach takes longer execution time, it due to that every individual in each generation must be decoded into a solution from optimised queue, and this process is very time-consuming. However, In GP, the initialisation first population is costly in time as transformation process from a DAG, but following new individuals are generated through mutation and crossover, which demands much less time comparing decoding process.

@@

\section{Conclusion}\label{conclusion}
This work introduces a comprehensive evaluation model employed our PSO-based method for QoS-aware automated semantic automated web service composition that combines the quality of semantic matchmaking with QoS. The results show that our approach obtain better functional quality with a reasonable trade-off in QoS. Also, we compare one GP-approach with our PSO-based method to show our performance results in finding better-optimised solution. Future works could investigate other direct or indirect representations of semantic web service composition on semantic web service composition, and look into other EC techniques to evaluate their performance. Also, we could reshape the problem on providing customers with a set of solutions to choose from, rather than a single solution, so research question is redefined as multi-objectives or many objective problems.

>>>>

\begin{document}
\maketitle
\begin{abstract}
Semantic web service composition has been a prevailing research area in recent years. There are two major challenges faced by researchers, semantic matchmaking and QoS optimisation. Semantic matchmaking aims to discover interoperable web services that can interact with each other to provide rich functionalities through language understanding and reasoning. QoS optimisation aims to optimise the non-functional requirement of service users, e.g., minimum cost, maximal reliability. Many scholars have looked into QoS optimisation problems in QoS-aware web service composition applying AI planning and Evolutionary Computation techniques. To meet users' requirement, one often needs to consider both semantic matchmaking quality and QoS simultaneously. Existing works on web service composition often concerns either semantic service composition or QoS-aware service composition. However, there are few works concerns both semantic matchmaking quality and QoS at the same time and achieve a more desirable tradeoff in consideration of both sides. Therefore, In this paper, proposed a general comprehensive quality model for semantic matchmaking quality and QoS. This model is also suitable to be tackled through EC algorithms, and we develop a PSO-based service composition approach with explicit support for the comprehensive model, which can generate a more desirable balanced web service composition that meet both semantic matchmaking quality and QoS requirement by comparing existing QoS evaluation model using benchmark dataset. We also conduct an experiment shows our PSO-based method performs better in finding more optimised solution by comparing one existing GP-based method.

@@

The overall goal of this paper is to \textit{develop an comprehensive approach to automated QoS-aware semantic web service composition that satisfactorily optimises both QoS and semantic matchmaking quality}. Particularly, this paper extends existing works of QoS-aware service composition by considering both QoS optimisation and semantic matchmaking quality optimisation in our proposed comprehensive quality model. Particle Swarm Optimisation (PSO) has show its promise in searching near-optimised service composition solutions \cite{da2016particle}. We will propose a PSO-based service composition approach using our comprehensive quality model to measure semantic matchmaking in automated semantic web service composition. We will achieve three objectives in this work as follows:

@@

 \item To evaluate our proposed approach, we conduct experiment to compare our comprehensive quality model with QoS evaluation model, we also compare an one existing GP approach with our approach using our comprehensive model. Both comparison utilise benchmark datasets from Web Services Challenge 2009 (WSC09) \cite{kona2009wsc}

@@

\section{Related Work} \label{relatedWork}
Substantial work on web service composition focused on either semantic web service composiiton \cite{boustil2014semantic,mier2015integrated, bansal2016generalized} or QoS-aware web service composiiton \cite{da2016particle,da2015graphevol,yu2013adaptive, gupta2015optimization,qi2010combining,ma2015hybrid}, However few researchers addressed both semantic mathmaking quality and QoS requirements at the same time for web service composition problems. To the best of our knowledge, \cite{lecue2009optimizing,fanjiang2014semantic,pop2009immune} reported some recent attempts on service composition that considers both aspects.

\cite{boustil2014semantic,mier2015integrated, bansal2016generalized} captures the semantics of the parameters of web services using some kind of logic (e.g., description logic) for enabling semantic web service composition, where the number of web services or length of the graph is minimised to reach the optimised graph-based composition solutions. However, these approaches always need to improve their scalability for a large number of web services, and the evaluation method does not fit for today's customers' requirements properly.

@@

Evolutionary Computation (EC) techniques are used to improve the scalability for solving NP-hard problems. Gupta et al. \cite{gupta2015optimization} employ an Genetic Algorithm to the problem of QoS-ware web service composition, and a set of binary strings are used as individuals, which demands to be decoded into composition solutions. Genetic Programming are employed by  \cite{yu2013adaptive} with direct representation of composition solutions, the overall quality of solutions are measured by a fitness function that is liable for penalising infeasible solutions. A hyper approach employs both a greedy search algorithm and Genetic Programming (GP) is introduced in \cite{ma2015hybrid} to generate locally optimised solution with functionality correctness. In particularly, the greedy search is used to generate directed acrylic graph as composition solutions, which is further transferred to tree structure using unfolding techniques for initialisation and mutation during the evolutionary process. To eliminating the transformation process from DAG, A promising GraphEvol is proposed in \cite{da2015graphevol}, where web service composition are in a form of Directed Acyclic Graph(DAG) employing Graph-based evolutionary operators like crossover and mutation. PSO has shown its efficiency in solving combinatorial optimisation problems \cite{fukuyama2008fundamentals}, an indirect PSO-based approach was introduced in \cite{da2016particle}. An optimised queue is used as indirect representation as composition solution that decoding into Direct Acyclic Graph (DAG). These QoS-aware approaches does not consider semantic matchmaking quality, which could lead to over-general outputs to be produced by selected services, The finding is evidently supported by our first comparison experiment. In fact, customers' perspectives, application domains and ontology granularity all could have significant impact on the outputs requested by users. In some scenarios, the output is too broad to bear any specific meaning for the customers, even though those web services selected leads to a very good overall QoS.

Few works \cite{lecue2009optimizing,fanjiang2014semantic,pop2009immune} employ EC technique for considering both semantic matchmaking quality and QoS simultaneously. Lecue et al. \cite{lecue2009optimizing} employ Genetic Algorithm for semi-automated web service composition considering semantic matchmaking quality and QoS, where the semantic matchmaking quality is measured the quality of semantic links that requires formal definition of ontology in Description logic. This evaluation takes huge cost and time for the domain experts to establish required ontology. Another GA-based approach work \cite{fanjiang2014semantic} employs a sequence of fitness functions are used in the binary selection of chromosomes, where semantic matchmaking quality is evaluate in two fitness functions considering concept similarity and parameter similarity respectively, However, different semantic matchmaking types are ignored in evaluation model. The work \cite{pop2009immune} as an immune-inspired web service composition approach employ indirect representation that a binary alphabet to encode a planning graph, where the semantic matchmaking quality is measured  by the similarity using information retrieval technique.

In summary, composition solutions from semantic web service composition does not consider QoS \cite{boustil2014semantic,mier2015integrated, bansal2016generalized}, and QoS-aware web service composiiton \cite{da2016particle,da2015graphevol,yu2013adaptive, gupta2015optimization,qi2010combining,ma2015hybrid} does not consider distinguished matchmaking quality in their fitness function. Few works do consider both quality aspects, but some limitations lie in semi-automated approach \cite{lecue2009optimizing}, less general semantic quality measurement \cite{lecue2009optimizing, pop2009immune}, or semantic matchmaking types ignorance \cite{pop2009immune}. In addition, experiments design for  \cite{lecue2009optimizing,fanjiang2014semantic,pop2009immune} are not conducted using benchmark dataset for the scalability, only small datasets are utilised that might suffer scalability. Results analysis for \cite{lecue2009optimizing,fanjiang2014semantic,pop2009immune} also do not evidently point out what desired balance could be reached by considering semantic matchmaking quality and QoS. Therefore, we proposed a general comprehensive quality model which achieve a more desirable balance in consideration of both semantic matchmaking quality and QoS to fill the gaps discussed above, and then we proposed a POS-based method with explicit support for the comprehensive model, and evaluate its performance by comparing with one existing GP-based approach.

@@

\subsection{Quality of Service and Composition Constructs}\label{Quality of Service and Composition Constructs}
According to \cite{zeng2003quality}, four most often considered QoS parameters are response time, cost, reliability and availability described as follows:
\begin{itemize}
\item \textit{Response time} ($T$) measures the expected delay in seconds between the moment when a request is sent and the moment when the results are received.
\item \textit{Cost} ($C$) is the amount of money that a service requester has to pay for executing the web service
\item \textit{Reliability} ($R$) is the probability that a request is correctly responded within the maximum expected time frame.
\item \textit{Availability} ($A$) is the probability that a web service is accessible.
\end{itemize}
The aggregation value of QoS attributes for a composite service varies with respect to different constructs, which reflects how services associated with each other in a service composition \cite{zeng2003quality}. Here we consider two composition constructs: sequence and parallel constructs, in building the composition web service. The QoS calculation models are described as follows:
\subsubsection{Sequence construct}
The composition web service executes each atomic service associated with a sequence construct in a definite sequence order. The aggregation value for total time ($T$) and total cost ($C$) is as the sum of time and cost of web services involved respectively. The overall availability and reliability in a sequence construct are calculated by multiplying their corresponding availability and reliability of each web service in probability theory. This construct is shown in Fig. \ref{sequence}.
\subsubsection{Parallel construct}
Web services in a parallel construct are executed concurrently. The QoS aggregation value for total cost, availability and reliability are the same as these in sequence construct while the Total time ($T$) is determined by the most time-consuming path in the composition flow of the solution. This construct is presented in Fig. \ref{parallel}.

@@

\textbf{Semantic web matchmaking quality model}. Due to the discretisational characteristics of different match types and values assigned to matching types that driven by the cost of data integration and manipulation \cite{lecue2009optimizing}, partial ordering match types are considered to be one factor for quality of parameter matchmaking, denoted as $mt_{p}$,  For example, Exact matching type demands less time for computation compared to that of Plugin match. Another factor in our proposed model is concept similarity, which could be evaluated based on the edge counting method defined in \cite{shet2012new}. This formula (\ref{equation1}) is used to estimate the concept similarity between matching parameters, which is denoted as $s_{p}$. Therefore, given the quality of parameter matchmaking type and quality of parameter concept similarity, the quality of parameter matchmaking is defined by Formula (\ref{equation2}), where the value of $mt_{p}$ follows the same settings in \cite{lecue2009optimizing}. Particularly, 1 (Exact), 0.75 (Plugin), 0.5 (Subsume) or 0.25 (Intersection).

\begin{equation}
s_{P}{=} \frac{2N \cdot e^{-\lambda L/D} }{N_{1}+N_{2}}
\label{equation1}
\end{equation}

@@

\section{Results and Analysis}\label{results_analysis}
\subsection{Comparison Test with QoS Evaluation Model}\label{comparisonTest}
QoS-aware web service composition \cite{da2016particle,da2015graphevol,yu2013adaptive,ma2015hybrid} do consider two semantic matchmaking types (Exact and Plugin) for discovering desired web service, but there is no measurement of matchmaking types and concept similarity, so the weights for $MT$ and $S$ are considered to be 0. Consequently, our evaluation mode become a widely used fitness function $Fitness = w_1 \hat{A} + w_2 \hat{R} + w_3(1 - \hat{T}) + w_4(1 - \hat{C})$ when $\sum_{i=1}^{4} w_i = 1$ \cite{ma2015hybrid} for QoS-aware web service composition. To compare the composition solution generated by using our approach comparing with QoS-aware approach. We look at mean value of $MT$, $S$ and $QoS$ at optimum at the 100th generation for two approaches. In QoS-aware approach, $MT$ and $S$ are recorded, and $QoS$ is normalised from 0 to 0.5 to make it comparable, besides that, all weights in QoS-aware fitness function are set equally to 0.25.

We observe an interesting pattern from Table \ref{decisionTable} using statistic analysis: mean value of $MT$ and $S$ at optimum by our approach is consistently higher than those by QoS-aware approach.  Meanwhile, $QoS$ generated by QoS-aware approach can achieve a more desirable tradeoff in both semantic matchmaking quality and  QoS.

\begin{table}[]
\footnotesize
\centering
\caption{Mean Quality for comprehensive quality-aware methods and QoS-aware approach}
\label{decisionTable}
\begin{tabular}{l|l|l|l}
\hline
\multicolumn{2}{c|}{WSC09}              & \shortstack{QoS-aware \\ Evaluation} & \shortstack{Comprehensive \\ Quality Evaluation} \\ \hline
\multirow{3}{*}{Task1}  &$MT$   &0.189787 $\pm$ 0.039278686            &0.221862 $\pm$ 0.009582 $\uparrow$ \\ \cline{2-4} 
                        &$S$    &0.884962 $\pm$ 0.014140               &0.894082 $\pm$ 0.009206 $\uparrow$ \\ \cline{2-4}
                        &$QoS$  &0.278730 $\pm$ 0.007786               &0.280222 $\pm$ 0.008212                          \\ \hline
\multirow{3}{*}{Task2}  &$MT$   &0.001795 $\pm$ 0.000719               &0.001977 $\pm$ 0.001566 $\uparrow$ \\ \cline{2-4} 
                        &$S$    &0.906971 $\pm$ 0.005855               &0.923970 $\pm$ 0.006898 $\uparrow$   \\ \cline{2-4}
                        &$QoS$  &0.239979 $\pm$ 0.000578 $\uparrow$    &0.238596 $\pm$ 0.001264 \\ \hline
\multirow{3}{*}{Task3}  &$MT$   &0.158526 $\pm$ 0.014028               &0.245830 $\pm$ 0.007761 $\uparrow$   \\ \cline{2-4} 
                        &$S$    &0.949109 $\pm$ 0.002331               &0.972765 $\pm$ 0.002980 $\uparrow$           \\ \cline{2-4}
                        &$QoS$  &0.247002 $\pm$ 0.000661 $\uparrow$    &0.245631 $\pm$ 0.000431            \\ \hline
\multirow{3}{*}{Task4}  &$MT$   &0.000000 $\pm$ 0.000000               &0.000004 $\pm$ 0.000002 $\uparrow$ \\ \cline{2-4} 
                        &$S$    &0.879514 $\pm$ 0.007456               &0.920733 $\pm$ 0.000001 $\uparrow$ \\ \cline{2-4}
                        &$QoS$  &0.242297 $\pm$ 0.000507 $\uparrow$    &0.236677 $\pm$ 0.002211  \\ \hline
\multirow{3}{*}{Task5}  &$MT$   &  0.000042 $\pm$ 0.000030             &0.000078 $\pm$ 0.000020 $\uparrow$           \\ \cline{2-4} 
                        &$S$    &  0.915933 $\pm$ 0.012888             &0.927678 $\pm$ 0.002578 $\uparrow$                 \\ \cline{2-4}
                        &$QoS$  & 0.238189 $\pm$ 0.000240 $\uparrow$      &  0.237485 $\pm$  0.000328  \\ \hline                                                   
\end{tabular}
\end{table}

To compare the results generated from two evaluation approaches, we demonstrate an example solution that shows the differences in web services composition obtained through two different methods. Fig. \ref{comparisontest} $(1)$ and $(2)$ show two composition weighted graphs as the two optimised solutions to Task 3 with $(1)$ QoS-aware approach and $(2)$ Comprehensive quality-aware method respectively. Two approaches generate exactly the same service workflow structure where those service vertices and edges denoted in red are different. We make a comparison of the quality among these different edges ($e_1$ to $e4$) associated service vertices in terms of quality of semantic matchmaking and QoS attributes in Fig. \ref{comparisontest} $(3)$. We also look at $\Delta Q$ which reveals the amount of variation on quality between two methods, where the positive values means the benefits gained under our approach while the negative values means the tradeoff. To demonstrate the benefits of the positive value, we analyse the smallest positive $\Delta Q$ corresponding to $e_4$ and demonstrate how the output and required input are different under two approaches in Fig. \ref{comparisontest} $(4)$. $Ser1640238160$ and $Ser1947554374$ are selected service vertices with output concept-related parameters $Inst795998200$ and $Inst582785907$ corresponding to two concepts $Con103314376$ and $Con2037585750$ respectively, and $Inst658772240$ are the required parameter related to concept $Con2113572083$. There exist $Inst795998200$ $\in$ $Con103314376$ $\sqsubseteq_{2}$ $Inst658772240$ $\in$ $Con2113572083$ and $Inst582785907$ $\in$ $Con2037585750$ $\sqsubseteq_{3}$ $Inst658772240$ $\in$ $Con2113572083$. It is obvious that our approach selects the service providing $Inst795998200$ that are closer to the users' requirements suggesting that our method can produce better semantic matchmaking quality in terms of less general outputs.

@@

\subsection{Comparison Test with GP-based approach}\label{comparisonTestWithGP}
To evaluate the performance of our proposed PSO-based approach, we compare one GP-based approach  \cite{ma2015hybrid} with our PSO method. We consider the links between child nodes and parent nodes as semantic web service links for semantic matchmaking quality, and those links information are maintained correctly for the crossover and mutation. Therefore, we evaluate both semantic matchmaking quality and QoS simultaneously using the proposed comprehensive quality model. To make a fair comparison with our PSO-based, we consider the same number of evaluations (3000 times), we set the parameters settings for GP-based approach \cite{ma2015hybrid}, 30 individuals and 100 generations.

The Table \ref{meanFitness} shows the mean fitness values accomplished by two methods. We employ statistical analysis to test the significant differences in mean fitness value.  The results show that the PSO-based approach performs better in four of five tasks.

@@

\section{Conclusion}\label{conclusion}
This work introduces a general comprehensive evaluation model that for considering semantic matchmaking quality and QoS. We proposed a PSO-based service composition approach utilising our proposed quality mode that can achieve a desired balance off of both quality aspects. Also, we compare one GP-approach with our PSO-based method to show our performance results in finding better-optimised solution. Future works can investigate multi-objective EC techniques to produce a set of composition solutions for the situations that quality preference is not known.
